### 2016-08-25 section/5_exper.tex
extract table

\begin{table}
  \centering
  %\scriptsize
  \tiny
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  $<0.01\%\pm0.73\%$  & $18.29\%\pm1.33\%$       &  $18.84\%\pm4.44\%$  & 355.51{\bf X}$\pm$8.59{\bf X} & 661.49{\bf X}$\pm$81.63{\bf X} \\ 
    Mozilla416628 &  $<0.01\%\pm1.76\%$  & $4.87\%\pm2.09\%$        &  $2.41\%\pm1.58\%$   & 72.52{\bf X}$\pm$1.57{\bf X}  & 112.15{\bf X}$\pm$2.01{\bf X} \\
    \midrule
     MySQL27287   &  $5.47\%\pm1.29\%$   & $0.20\%\pm2.04\%$        &   -                  & 263.74{\bf X}$\pm$8.50{\bf X} & 880.95{\bf X}$\pm$101.24{\bf X} \\
     MySQL15811   &  -                   & $0.35\%\pm2.81\%$        &   -                  & 413.59{\bf X}$\pm$53.94{\bf X}& 1087.16{\bf X}$\pm$43.26{\bf X} \\
    \midrule
      GCC46401    &  $<0.01\%\pm0.17\%$  & $<0.01\%\pm0.27\%$       &  $<0.01\pm0.22\%$    & 32.89 {\bf X}$\pm$0.38{\bf X} & 59.07{\bf X}$\pm$1.24{\bf X}\\ 
      GCC1687     & -              & /                 &  $1.84\%\pm0.28\%$                &   /                           & 223.30{\bf X}$\pm$17.75{\bf X} \\
      GCC27733    & $<0.01\%\pm0.26\%$   & /           &  $<0.01\%\pm0.25\%$               &   /                           & 18.44{\bf X}$\pm$0.32{\bf X}     \\
      GCC8805     & -              & $0.50\%\pm1.26\%$ &  $0.19\%\pm1.43\%$                & 2.89{\bf X}$\pm$0.35{\bf X}    & 3.36{\bf X}$\pm$0.44{\bf X}\\
      GCC21430    & -              & $4.86\%\pm0.81\%$ &  $2.37\%\pm1.38\%$                & 164.02{\bf X}$\pm$20.35{\bf X} & 254.9{\bf X}$\pm$22.34{\bf X} \\
      GCC12322    & -              & $4.77\%\pm2.48\%$ &  $<0.01\%\pm2.24\%$               & 25.56{\bf X}$\pm$2.50{\bf X}  & 24.87{\bf X}$\pm$2.52{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop
    (only non-extracted benchmarks are shown). 
  -: dynamic analysis is not needed;
  /: not applicable.}
  \label{tab:performance}
\end{table}

>>>>

\input section/overhead_tab.tex
